---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "STONE.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: fn03_STONE.qmd
File name html: fn03_STONE.html


```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "../AAA_fn/fn_actions.R")
source(file = "../AAA_fn/fn_extract.R")

```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_stone_html <- "STONE.html"
   str_qmd_file_name <-     "f00_01_RQuarto.qmd"
   str_new_qmd_file_name <- "f00_01_RQuarto.qmd"
   str_file_name_Rscript_external <- "zzz_output_f02_gen_Rscript_external.R"
   str_file_name_Rscript_internal <- "zzz_output_f02_gen_Rscript_internal.R"
   
# Folders
   str_folder_input_external  <- "../f00_03_MOD_code"
   str_folder_output_external <- "../zzz_zzz_output"
   str_folder_output_local    <- "zzz_output_local"

# Paths
   str_qmd_file_path_input_external <- file.path(str_folder_input_external, str_qmd_file_name)
   str_qmd_file_path_local_OLD          <- file.path(str_folder_output_local, str_qmd_file_name)
   str_qmd_file_path_local_NEW          <- file.path(str_folder_output_local, str_new_qmd_file_name)
  
   str_file_path_Rscript_external <- file.path(str_folder_output_local, str_file_name_Rscript_external)
   str_file_path_Rscript_internal <- file.path(str_folder_output_local, str_file_name_Rscript_internal)

str_folder_TO <- str_folder_output_local
    
```

# Basics status and cleaning.


## Checking Hidden Runner HTML file at local folder.
::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_file_stone_html)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```


## Checking output folder local.
::: {.callout-note}
Folder must exists and be clean.
::: 
```{r step01_02_01, eval=TRUE, echo=FALSE, results='asis'}
step01_04_01 <- function(){
  
  the_output <- fn_check_and_create_and_clean_single_folder(str_folder_path = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step01_04_01()
```


```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
step9923_03_01 <- function(){
the_output <- fn_copy_verify_single_file(str_file_path_from = str_qmd_file_path_input_external, 
                           str_file_path_to = str_qmd_file_path_local_NEW)

if(!the_output) knitr::knit_exit()
}
  step9923_03_01()
```

---



# Create R script internal
::: {.callout-note}
From all ours .qmd files, we will create a .R file to use internal.  
This file is not for final user.

:::


## Create File Rscript internal
```{r step05_02_02, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

vector_qmd_code_path_internal <- c(str_qmd_file_path_local_NEW)

step05_02_02 <- function() {
  # 1. Encabezado visual (Siguiendo tu estándar)
  cat("<b>Code Extraction & Concatenation</b><br>")
  cat(paste0("<small style='color: #6c757d; font-style: italic;'>Action: Extracting chunks with <code>code_internal = TRUE</code> into a single .R file.</small><br>"))
  
  # 2. Ejecución de la lógica de R (La función que ya tenemos)
  # Guardamos el resultado booleano
  the_output <- fn_extract_and_concatenate_code(
    vector_files    = vector_qmd_code_path_internal, 
    str_output_path = str_file_path_Rscript_internal, 
    marker_string   = "code_internal\\s*=\\s*(TRUE|T)"
  )

  # 3. Salida visual según el resultado (TRUE/FALSE)
  if (the_output) {
    # CASO ÉXITO
    cat("<span style='color: #28a745;'>✔ <b>Success:</b> Code extracted and master script generated successfully.</span><br><br>")
    # return(TRUE) # Retorno para autoprint
    
  } else {
    # CASO ERROR
    cat("<span style='color: #dc3545;'>✘ <b>Critical Error:</b> Code extraction failed or no matches found.</span><br>")
    cat("<small style='color: #6c757d;'>Check the console messages for technical details.</small><br><br>")
    
    # 4. Corte de ejecución si falla
    knitr::knit_exit()
  }
}

# Ejecución
step05_02_02()

```

```{r step05_02_03, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 1. Carga inicial

step05_02_03 <- function(){
the_output <- fn_check_single_file(str_file_path = str_file_path_Rscript_internal)
if(!the_output) knitr::knit_exit()
}
step05_02_03()
```



# Create R script external
::: {.callout-note}
From all ours .qmd files, we will create a .R file to use externaly.  
This file is for final user.

## Create File Rscript external



```{r step06_02_02, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}


vector_qmd_code_path_external <- c(str_qmd_file_path_local_NEW)
step06_02_02 <- function() {
  # 1. Encabezado visual (Siguiendo tu estándar)
  cat("<b>Code Extraction & Concatenation</b><br>")
  cat(paste0("<small style='color: #6c757d; font-style: italic;'>Action: Extracting chunks with <code>code_external = TRUE</code> into a single .R file.</small><br>"))
  
  # 2. Ejecución de la lógica de R (La función que ya tenemos)
  # Guardamos el resultado booleano
  the_output <- fn_extract_and_concatenate_code(
    vector_files    = vector_qmd_code_path_external, 
    str_output_path = str_file_path_Rscript_external, 
    marker_string   = "code_external\\s*=\\s*(TRUE|T)"
  )

  # 3. Salida visual según el resultado (TRUE/FALSE)
  if (the_output) {
    # CASO ÉXITO
    cat("<span style='color: #28a745;'>✔ <b>Success:</b> Code extracted and master script generated successfully.</span><br><br>")
    # return(TRUE) # Retorno para autoprint
    
  } else {
    # CASO ERROR
    cat("<span style='color: #dc3545;'>✘ <b>Critical Error:</b> Code extraction failed or no matches found.</span><br>")
    cat("<small style='color: #6c757d;'>Check the console messages for technical details.</small><br><br>")
    
    # 4. Corte de ejecución si falla
    knitr::knit_exit()
  }
}

# Ejecución
step06_02_02()

```



```{r step06_02_03, eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
# 1. Carga inicial

step06_02_03 <- function(){
the_output <- fn_check_single_file(str_file_path = str_file_path_Rscript_external)
if(!the_output) knitr::knit_exit()
}
step06_02_03()
```








# Export zzz_output files and folders.
```{r step_export, eval=TRUE, echo=FALSE, results='asis'}
the_output <- fn_export_files_zzz_output(str_file_path_from = str_folder_output_local, 
                                         str_file_path_to = str_folder_output_external,
                                         bln_overwrite = FALSE,
                                         bln_production = TRUE)
if(!the_output) knitr::knit_exit()
```




# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```

