---
title: "Rscience - Hidden Runner"
format: 
  html: 
    output-file: "STONE.html"
    embed-resources: true
    number-sections: true
    number-depth: 3
    include-in-header:
      text: |
        <style>
        h1, h2, .title {
          border-bottom: none !important;
          margin-bottom: 10px;
        }
        </style>
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
File name qmd: STONE.qmd
File name html: STONE.html

```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}

 #Cargar configuración desde _quarto.yml
library("yaml")
library("quarto")
library("fs") 
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
source(file = "../AAA_fn/fn_actions.R")
source(file = "../AAA_fn/fn_extract.R")
source(file = "../AAA_fn/fn_run.R")

```

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
    str_file_name_RData_internal_file <- "zzz_output_fn04_RData.RData"
    str_file_hidden_runner_html_file <- "STONE.html"
    str_stone_gen_report_qmd_file <-     "RUNNER.qmd"
    str_stone_gen_report_old_html_file <- "RUNNER.html"
    str_stone_gen_report_new_html_file <- paste0("zzz_output_f06_", str_stone_gen_report_old_html_file)

# Folders
    str_folder_output_local    <- "zzz_output_local"
    str_folder_stone           <- "files"
    str_folder_output_external <- "../zzz_zzz_output"

# Paths
    str_file_name_RData_internal_path <- file.path(str_folder_output_external, str_file_name_RData_internal_file)
    str_stone_gen_report_qmd_path <- file.path(str_folder_stone, str_stone_gen_report_qmd_file)
    str_stone_gen_report_old_html_path <- file.path(str_folder_stone, str_stone_gen_report_old_html_file)
    str_stone_gen_report_new_html_path <- file.path(str_folder_output_local, str_stone_gen_report_new_html_file)

```

# Basics status and cleaning.
## Checking Hidden Runner HTML file at local folder.
::: {.callout-note}
File HTML hidden-runner must not exists or be deleted previous execution.
::: 
```{r step01_01_01, eval=TRUE, echo=FALSE, results='asis'}
step01_01_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_file_hidden_runner_html_file)
  if(!the_output) knitr::knit_exit()
}
step01_01_01()
```


## Output local folder.

::: {.callout-note}
Must exists a <code>`r str_folder_output_local`</code> at local folder and must be empty before render files.
::: 

```{r step01_03_01, eval=TRUE, echo=FALSE, results='asis'}
step01_03_01 <- function(){
  
    the_output <- fn_check_and_create_and_clean_single_folder(str_folder_path = str_folder_output_local)
 
  if(!the_output) knitr::knit_exit()
}
step01_03_01()
```




## Stone folder.

::: {.callout-note}
Must exists a <code>`r str_folder_stone`</code> at local folder.
::: 

```{r step01_04_01, eval=TRUE, echo=FALSE, results='asis'}
step01_04_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_path = str_folder_stone)
  if(!the_output) knitr::knit_exit()
}
step01_04_01()
```

## Render output file
```{r step01_05_01, eval=TRUE, echo=FALSE, results='asis'}
step01_05_01 <- function(){
  
  the_output <- fn_delete_single_file(str_file_path = str_stone_gen_report_old_html_path)
  if(!the_output) knitr::knit_exit()
}
step01_05_01()
```


## External output folder.

::: {.callout-note}
Must exists a <code>`r str_folder_output_external`</code> at local folder.
::: 

```{r step01_06_01, eval=TRUE, echo=FALSE, results='asis'}
step01_06_01 <- function(){
  
  the_output <- fn_check_single_folder(str_folder_path = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step01_06_01()
```








# Rendering RQuarto 
```{r step02_01_01, eval=TRUE, echo=FALSE, results='asis'}
step02_01_01 <- function(){
  
  library("quarto")
    # str_RQuarto_html_old_path
  quarto::quarto_render(input = str_stone_gen_report_qmd_path, 
                        execute_dir = dirname(str_stone_gen_report_qmd_path), 
                        quiet = F)
  
  the_output <- fn_check_single_file(str_file_path = str_stone_gen_report_old_html_path)
  if(!the_output) knitr::knit_exit()
    
  
  the_output <- fn_rename_single_file(str_file_path_from = str_stone_gen_report_old_html_path, 
                                      str_file_path_to = str_stone_gen_report_new_html_path)

  if(!the_output) knitr::knit_exit()
}
step02_01_01()
```


# Export zzz_output files and folders.
```{r step_export, eval=TRUE, echo=FALSE, results='asis'}
the_output <- fn_export_files_zzz_output(str_file_path_from = str_folder_output_local, 
                                         str_file_path_to =   str_folder_output_external,
                                         bln_overwrite = FALSE,
                                         bln_production = TRUE)
if(!the_output) knitr::knit_exit()
```


# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)



# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```



