---
title: "Rscience"
format: 
  html: 
    output-file: "action01_STONE.html"
    embed-resources: true
execute: 
  enabled: true
---

Tool: Rs003_LM_QQ_FIX_BAL_ANOVA_1Way_s001  
QMD File name: action01_STONE.qmd

This qmd:  
- Clears the environment.  
- Locates the original file.  
- Generates a copy.  
- Applies the "my_variable" modifications.  
    
```{r step00_time_start, eval=TRUE, echo=FALSE, results='asis'}
# Captura del tiempo inicial
time_start <- Sys.time()

cat("<b>Runner Execution Started:</b>", format(time_start, "%Y-%m-%d %H:%M:%S"), "<br>")
cat("<hr>")
```

```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Libraries
library("fs")
library("knitr")
library("tidyverse")
library("kableExtra")

# Funtions
# source(file = "fn_local.R")
source(file = "../AAA_fn/fn_actions.R")
```

---

```{r basics, eval=TRUE, echo=FALSE, results='asis'}
# Files
   str_file_hidder_runner_html <- "action01_STONE.html"
   str_old_qmd_file_name <-       "f00_01_RQuarto.qmd"
   str_new_qmd_file_name <-       "f00_01_RQuarto.qmd"
   
# Folders
   str_folder_input_external  <- "../f00_01_BankCode"
   str_folder_output_external <- "../f00_03_MOD_code"
   str_folder_output_local    <- "zzz_output_local"

# paths
   str_path_old <- file.path(str_folder_output_local, str_old_qmd_file_name)
   str_path_new <- file.path(str_folder_output_local, str_new_qmd_file_name)

```




```{r eval=TRUE, echo=FALSE, message=FALSE, warning=FALSE}
# Folders
str_folder_FROM <- str_folder_input_external
str_folder_TO <- str_folder_output_local
str_folder_TO_external  <- str_folder_output_external

vector_qmd_file_paths_FROM <- list.files(path = str_folder_FROM , 
                                            pattern = "\\.qmd$", 
                                            full.names = T)
vector_qmd_file_names <- basename(vector_qmd_file_paths_FROM)

vector_qmd_file_paths_TO <- file.path(str_folder_TO, vector_qmd_file_names)
vector_qmd_file_paths_TO_external <- file.path(str_folder_TO_external, vector_qmd_file_names)


```


# Checking input folder and files (FROM)
## FROM files: files must exists.
```{r step91_01_01, eval=TRUE, echo=FALSE, results='asis'}

step91_01_01 <- function(){
  

the_output <- fn_check_multi_files(vector_file_path = vector_qmd_file_paths_FROM)

    if(!the_output) knitr::knit_exit()
}
step91_01_01()
```


# Checking external output folder
```{r step02_03_01, eval=TRUE, echo=FALSE, results='asis'}

step02_03_01 <- function(){
  
  the_output <- fn_check_and_create_and_clean_single_folder_SUPER_POWER(str_folder_path = str_folder_output_external)
  if(!the_output) knitr::knit_exit()
}
step02_03_01()
```


# Checking local output folder
```{r step992_03_01, eval=TRUE, echo=FALSE, results='asis'}

step992_03_01 <- function(){
  
  the_output <- fn_check_and_create_and_clean_single_folder(str_folder_path = str_folder_output_local)
  if(!the_output) knitr::knit_exit()
}
step992_03_01()
```




# Copying files FROM-TO.  (external to outpuit local)
```{r step02_05_01, eval=TRUE, echo=FALSE, results='asis'}

step02_05_01 <- function(){
  
the_output <- fn_copy_verify_multi_files(vector_from_file_path = vector_qmd_file_paths_FROM, 
                           vector_to_file_path = vector_qmd_file_paths_TO)
if(!the_output) knitr::knit_exit()
}
step02_05_01()
```


## Verify existence after copy on TO.
```{r step02_05_02, eval=TRUE, echo=FALSE, results='asis'}

step02_05_02 <- function(){
  
the_output <- fn_check_multi_files(vector_file_path = vector_qmd_file_paths_TO)
if(!the_output) knitr::knit_exit()
}
step02_05_02()
```


## Aplicando los cmaibos en los archivos de local output
```{r sssss222, eval=TRUE, echo=FALSE, results='asis'}

# 
# step302_05_02 <- function(){
#   
# the_output <- fn_rename_single_file(str_file_path_from = str_path_old,
#                                     str_file_path_to = str_path_new)
# if(!the_output) knitr::knit_exit()
# }
# step302_05_02()
```


   
# Copying files FROM-TO.  (local output to external local)
```{r step02_05_0122, eval=TRUE, echo=FALSE, results='asis'}

step02_05_0122 <- function(){
  
the_output <- fn_copy_verify_multi_files(vector_from_file_path = vector_qmd_file_paths_TO, 
                           vector_to_file_path = vector_qmd_file_paths_TO_external)
if(!the_output) knitr::knit_exit()
}
step02_05_0122()
```


## Verify existence after copy on TO.
```{r step02_05_02333, eval=TRUE, echo=FALSE, results='asis'}

step02_05_02333 <- function(){
  
the_output <- fn_check_multi_files(vector_file_path = vector_qmd_file_paths_TO_external)
if(!the_output) knitr::knit_exit()
}
step02_05_02333()
```

# Final Summary
```{r step_final_time_end, eval=TRUE, echo=FALSE, results='asis'}
# 1. Cálculos de tiempo
time_end <- Sys.time()
time_duration <- difftime(time_end, time_start, units = "auto")
str_duration <- format(time_duration, digits = 3)

# 2. Conteo de archivos
total_out <- length(list.files(str_folder_output_local, pattern = "^zzz_output_"))

# 3. Construcción del HTML (Asegurando que no haya espacios extraños al inicio)
html_summary <- paste0(
  "<hr>",
  "<div style='background-color: #f8f9fa; border: 1px solid #dee2e6; padding: 15px; border-radius: 5px; font-family: sans-serif; color: #333;'>",
  "  <b style='display: block; color: #495057; font-size: 1.1em; margin-bottom: 10px;'>🏁 Final Execution Summary</b>",
  "  <div style='margin-bottom: 5px;'>🕒 <b>Start Time:</b> ", format(time_start, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>🏁 <b>End Time:&nbsp;</b> ", format(time_end, "%H:%M:%S"), "</div>",
  "  <div style='margin-bottom: 5px;'>⌛ <b>Total Duration:</b> <span style='color: #007bff; font-weight: bold;'>", str_duration, "</span></div>",
  "  <div style='margin-bottom: 5px;'>📦 <b>Generated Files:</b> ", total_out, " files in local output</div>",
  "</div>",
  "<div style='text-align: center; margin-top: 10px;'><small style='color: #6c757d;'>End of Rscience Automated Runner</small></div>"
)

# Usamos cat con fill = TRUE para asegurar que el buffer se limpie correctamente
cat(html_summary, fill = TRUE)
```
